Molecular dynamics simulation of synchronization in driven particles

### 2020-12-17 manuscript/manuscript_ajp_2020.tex
added reference

\section{Introduction} %
%
%Outline
%------------------------------------------------------------------
%synchronization = widest audience possible
Synchronization is a universal phenomena
that can be modeled with numerical studies of confined 
driven particles.
%Christiaan Huygens 
%[has been adapted into many useful technologies...]
Examples of synchronization occur
in many naturally oscillating systems,
from Huygens 1665 observation of
in-phase oscillation of pendulum clocks \cite{Pikovsky2003},
to fireflies signaling in time with a pulsed light emitting diode \cite{},
to coordinated flapping of birds wings \cite{},
to simultaneous neuronal firing in cardiac muscle \cite{}
and brain tissue \cite{}.

@@

>>>>

\section{Introduction} %
%
%Outline
%------------------------------------------------------------------
%synchronization = widest audience possible
Synchronization is a universal phenomena
that can be modeled with numerical studies of confined 
driven particles.
%Christiaan Huygens 
%[has been adapted into many useful technologies...]
Examples of synchronization occur
in many natural periodic systems,
from Huygens 1665 observation of
in-phase oscillation of pendulum clocks \cite{Pikovsky2003},
to fireflies signaling in time with a pulsed light emitting diode \cite{},
to coordinated flapping of birds wings \cite{},
to simultaneous neuronal firing in cardiac muscle \cite{}
and brain tissue \cite{}.

@@

\bibitem{Pikovsky2003} A. Pikovsky, M. Rosenblum, and J. Kurths, {\it Synchronization: A Universal Concept in Nonlinear Sciences} (Cambridge Univ. Press, Cambridge, 2003).
